---
title: "Welcome to The Open Inference Lab"
listing:
  id: recent-posts
  contents: posts
  feed: true
  sort: "date desc"
  type: grid           
  max-items: 3
  categories: true
  sort-ui: false
  filter-ui: false
  grid-columns: 3 
page-layout: full
title-block-banner: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

A place for exploring statistical models, with a focus on making complex methods more transparent and easier to understand. Here you’ll find notes, examples, and code on Bayesian modeling, multivariate analysis, statistical decision-making, and anything else I have on my (academic) mind.

The goal is to open up the “black box” of some modern, complex statistical methods. How do these models actually work? And what do their results really tell us?

Most posts are grounded in practical examples using R. Along the way, there’s room for reflections.

Whether it’s unpacking a model, comparing approaches, or walking through an analysis step by step—this is a space to think carefully about inference. While starting with the models I know most about (obviously the models I worked on myself), in the future, I will start to discuss other models and techniques as well.

Do you have some topic in mind that you would like me to discuss? Let me know!

```{r contact, echo = FALSE, results = 'asis'}
library(fontawesome)

cat(paste0(
  '<div style="display:flex; gap:20px;">',
  
  '<a href="https://github.com/XynthiaKavelaars/bmco" target="_blank">',
  fa("github"), ' Github</a>',

  '<a href="https://bsky.app/profile/xynthia-kavelaars.bsky.social" target="_blank">',
  fa("bluesky"), ' BlueSky</a>',
  
  '<a href="https://mastodon.social/@xynthiakavelaars" target="_blank">',
  fa("mastodon"), ' Mastodon</a>',
#  
#  '<a href="https://mastodon.social/@xynthiakavelaars" target="_blank">',
#  fa("blog"), ' Blog</a>',
  
  '<a href="www.linkedin.com/in/xynthia-kavelaars-7a0377129" target="_blank">',
  fa("linkedin"), ' LinkedIn</a>', 

  '<a href="https://orcid.org/0000-0003-1600-3153" target="_blank">',
  fa("orcid"), ' ORCID</a>', 

  '</div>'
))
```

```{=html}
<br>
<br>
```

## Recent posts

::: {#recent-posts}
:::
